--- 
title: "Essential Workshop Preparation"
---

It is essential you have R and RStudio installed, and BYO laptop for the course. 

[Install R (>= 4.3.0)](https://cran.ms.unimelb.edu.au/)

[Install RStudio](https://rstudio.com/products/rstudio/download/)

Please make sure all packages are installed prior to the workshop.

Install/update BiocManager to version 3.18.

```{r, eval=FALSE}
install.packages("BiocManager") 
BiocManager::install(version = "3.18") 
```

Then install the packages. 
```{r, eval=FALSE}
BiocManager::install("SPIAT") 
BiocManager::install("spaSim") 
```

And these packages:
```{r, eval = FALSE}
install.packages(c("elsa", "Rtsne", "umap", "alphahull", "plotly", "survminer", 
                   "survival", "vroom", "rmarkdown", "knitr"))
BiocManager::install("ComplexHeatmap")
```

If asked to update all/some/none packages, please answer with a. 

If asked to install the compilation packages, please answer with Yes. 

**Note**: If you don’t want to change your current library, it’s better to create a new R project and use the package `renv` (https://rstudio.github.io/renv/articles/renv.html) to install the packages for this workshop. 

Please email yuzhou.feng@petermac.org if you have any issue installing the packages.

